### 2020-05-12 README.Rmd
Simplified the output directory structure and cleaned up all related files and vignettes. No Errors, Warnings, Notes (No EWN)

Of course, adding such a component increases the number of options that may need to be explored, but currently we envisage including a very low, a middle range, and a relatively high level of larval dispersal, to examin its implications.

@@

``` r
# install.packages("devtools")
devtools::install_github("haddonm/aMSE")
devtools::install_github(haddonm/rutilsMH) # also useful for plotting, etc
```

@@

```{r example}
# basic example code
library(aMSE)
library(rutilsMH)

  data(region1)
  glb <- region1$globals
  data(testregC)
  data(testregD)
  regDe <- testequil(regC=testregC,regD=testregD,glob=glb)
  str(regDe)

>>>>

Of course, adding such a component increases the number of options that may need to be explored, but currently we envisage including a very low, a middle range, and a relatively high level of larval dispersal, to examine its implications.

@@

```{r echo=TRUE, eval=FALSE}
if (!require(devtools)){install.packages("devtools")}

devtools::install_github("https://github.com/haddonm/aMSE",build_vignettes = TRUE)
```

@@

```{r example}
# a minimal example
starttime <- as.character(Sys.time())
library(aMSE)
# Obviously you should modify the resdir to suit your own computer
resdir <- "./../../rcode2/aMSEUse/out/testrun"
dirExists(resdir,make=TRUE,verbose=TRUE)
# You now need to ensure that there is a control.csv, reg1smu2pop6.csv
# and region1.csv file in the data directory
ctrlfiletemplate(resdir)  # puts a template ctrlfile into resdir
regionfiletemplate(resdir)  # puts a template region file into resdir
datafiletemplate(6,resdir,filename="reg1smu2pop6.csv") # etc
ctrl <- checkresdir(resdir) # checks the data files are present
runname <- ctrl$runlabel    # and reads the control file, if present
region1 <- readregionfile(resdir,ctrl$regionfile)
glb <- region1$globals
constants <- readdatafile(glb$numpop,resdir,ctrl$datafile)

out <- setupregion(constants, glb, region1) # make operating model 
regionC <- out$regionC     # constant bits
regionD <- out$regionD     # dynamics bits
product <- out$product     # all usually saved in resdir, not here
  # did the larval dispersal level disturb the equilibrium?
regDe <- testequil(regionC,regionD,glb)

resfile <- setuphtml(resdir,runname)# prepare to save and log results

plotproductivity(resdir,runname,product,glb)
biology_plots(resdir, runname, glb, regionC)
numbersatsize(resdir, runname, glb, regionD)

endtime <- as.character(Sys.time())

reportlist <- list(runname=runname,
                   starttime=starttime,endtime=endtime,
                   regionC=regionC, regionD=regionD, product=product,
                   glb=glb,constants=constants
)

runnotes <- "This is a bare-bones example."
# If you unhash the make_html component it will generate a local 
# website inside resdir and open it so you can see the results so far.
#
# make_html(replist=reportlist,resdir=resdir,width=500,
#          openfile=TRUE,runnotes=runnotes,verbose=FALSE)
